\section{Problema examen 3}
\subsection{Enunciat}
\textbf{Surveillance.} The Barcelona Diagonal University campus is shared among the UPC, UB, CSIC, and other public and private entities. As a result there are many surveillance cameras placed outside the buildings whose images can be accessed by different surveillance companies and in some cases by different surveillance teams inside the company. Each camera has a unique surveillance team that can visualize the images on the spot. The UPC Chancellor needs to establish a surveillance plan to be set during the next Chancellor elections. The aim of the plan is to guarantee that the voting is done without pressure. 

To establish the plan the UPC Committee has set a collection of \textit{surveillance locations} that require visual surveillance. For each of those locations, they have collected the surveillance teams that have cameras visualizing the location. Fortunately all the surveillance locations can be covered by an already existing camera, so the task can be performed without additional infrastructure.

Due to the economical situation, the UPC Chancellor wants to expend the minimum possible amount of money. The administrative office has negotiated and agreed the surveillance cost with each of the surveillance teams. Now they are seeking a solution that allows to keep surveillance on all the selected surveillance locations with minimum total cost. Assume, for this exercise, that a surveillance team receives a fix amount of money for looking to the images of all the cameras assigned to it.

\vspace{5mm}
(a) Design a constant factor approximation algorithm for the problem. Justify its correctness and efficiency. 

\vspace{5mm}
(b) Prove that the decision version of the variant of the problem in which the cost of all surveillance teams is the same belongs to $W[1]$. To prove this result use the number of selected surveillance teams as the parameter.

\subsection{Solució}